KidsAIR wood stove grades and usage

### 2020-11-10 stove_grade_usage_cleaning.Rmd
main analysis updates

##### WMT #####
# Load data
kw_report_wmt <- read_csv(paste0(file_path, "Input/WMT/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "WMT") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

@@

##### NN #####
# Load data
kw_report_nn <- read_csv(paste0(file_path, "Input/NN/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "NN") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

@@

##### AK #####
# Load data
kw_report_ak <- read_csv(paste0(file_path, "Input/AK/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "AK") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

>>>>

##### WMT #####
# Load data
kw_report_wmt <- read_csv(paste0(file_path, "Input/WMT/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         filter_type = as.character(FType),
         area = "WMT") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, filter_type, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

@@

##### NN #####
# Load data
kw_report_nn <- read_csv(paste0(file_path, "Input/NN/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         filter_type = as.character(FType),
         area = "NN") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, filter_type, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

@@

##### AK #####
# Load data
kw_report_ak <- read_csv(paste0(file_path, "Input/AK/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         filter_type = as.character(FType),
         area = "AK") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, filter_type, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)
